% Created:  
% Author:   Julie Sewards
% Filename: background.tex

\chapter{Background Material}
\label{cha:background}

In this chapter we will introduce some key aspects of the android architecture and its security features.  We will also examine the features offered by the Dropbox API and finally we will look briefly at some of the commercial applications which were reviewed as part of our initial research and which offer some features similar to Securely Share.

\section{Android Security Features}

Android provides an open source platform and application environment for mobile devices.  It has a layer based architecture whose foundational component  is the Android Operating System.  Based on the tried and tested Linux 2.6 kernel and modified by Google to include some additional features, it is the comprehensive user permissions model inherent in Linux that is responsible for providing the separation between applications that is a key feature of Android security.  At installation time, each application is assigned a unique user ID (UID);at runtime each application is run as a separate process an as a separate user with its given UID. This creates an Application Sandbox, protecting any resources belonging to that application (memory space, files, etc.) from being accessed by another application unless specifically permitted to do so by the developer.







Cryptography
Android provides a set of cryptographic APIs for use by applications. 















\section{Dropbox API}
\label{sec:dropbox}
Dropbox is a cloud storage service that also offers users  automatic backup facilities, file synchronization across devices, and the ability to share files with other users.  It provides multi-platform client applications plus a series of public APIs that enable different subsets of the Dropbox functionality to be integrated into third-party applications.  

On the Android platform, Dropbox offers three APIs, described on its website as follows:-:
\begin{description}
	\item[Core]The Core API includes the most comprehensive functionality including features such as search, file restore, etc. Although more complex than either of the other two to implement, it is often more suitable when developing server-based apps.
	\item[Datastore]The Datastore API provides a means of storing and synchronizing structured data like contacts, to-do items, and game states across  all the user's devices.
	\item[Sync]The Sync API provides a file system for accessing and writing files to the user's Dropbox.  The Sync API manages the process of synchronizing file changes to Dropbox and can also provide the app with notification when changes are made to files stored on the server.
\end{description}

For the purposes of the SecurelyShare app, although it offers the most basic interface to the Dropbox server, the Sync API was deemed to support both the functionality required for the prototype and some additional facilities which could be implemented at a later date in order to improve the overall user experience.

Each app on the Dropbox Platform needs to be registered in the App Console and the developer needs to select which permissions the app requires. These permissions determine the type of data that the app can access in the user's Dropbox.  For the Sync API, three levels of permission were applicable:
\begin{itemize}
\item App folder:  this creates a folder in the user's Dropbox with the same name as the app, all files relating to the app are kept here and access is restricted to this folder and its subfolders.
\item File type: the app is given access to the user's entire Dropbox but is restricted only to seeing files of certain types (documents, images, ebooks, etc.)  
\item Full Dropbox:  the app is given unrestricted access to the user's Dropbox

\end{itemize}



\section{Review of Related Products}

One of the security claims of cloud storage provider, Dropbox, is that user data stored on their servers is  fragmented and encrypted using 256-bit AES.  However, although users may feel reassured by these claims, it is also to be noted that since this encryption is applied server-side, the servers also have access to the keys required to decrypt this information.  Furthermore, the   Dropbox privacy policy states that,  
\begin{quotation}
"We may disclose your information to third parties if we determine that such disclosure is reasonably necessary to (a) comply with the law; (b) protect any person from death or serious bodily injury; (c) prevent fraud or abuse of Dropbox or our users; or (d) protect Dropbox's property rights. 
\end{quotation} 

It may therefore come as little surprise that there are an increasing  number of client-side encryption applications available that  integrate with Dropbox and other similar cloud services  to ensure that, even if files are disclosed, the organisations concerned would have no access to decryption keys.

Although there are a significant number of encryption applications available, our research was not able to identify any robust security comparison of the various products on offer.  We decided to consider two commercially produced applications, Boxcryptor and SafeMonk 

When trying to evaluate these products there appeared to be a paucity of robust reviews from respected members of the security fraternity and many of the review that were available seemed to focus more on the usability of applications rather than on their security features.  One of the only ways that a security application can truly be evaluated is if the source code is available for community scrutiny as security flaws often fail to come to light just from using the product.  Most of the products we looked at seemed to be designed primarily for personal file protect - some professed to offer sharing although some of the less polished versions required manual sharing of encryption keys.  Some of them were unforthcoming about exactly how they work

Two products that we examined in greater details, partly because they seemedto be higher profile products although that may simply be due to the fact that they were commercial products with a paid version as well as the free version that we tested and hence had larger marketing budgets.  It may also be because they had more security credibility however there was a common trend among the examined applications to use AES for encryption of the actual files themselves and some implementation of RSA to manage the key exchange,  In all the cases that we examined there was a central server that was used for key management, although both Boxcryptor and Safemonk were keen to strees that they were "tapproof" or "zero-knowledge" servers and had no access to key material that would enable them to decrypt user files.  There justification for storing the user's private key on the server was that it would allow the user to install the application on multiple devices and they both used password-based encryption (PBE) in order to secure the key on the server.  Although the servers use key-stretching algorithms to derive the encryption keys, we should always be aware that users can be very poor at choosing strong passwords and at keeping them secure. (In a study of password reuse, Bonneau \cite{das2014tangled} observed that 43 percent of  users reused a password across multiple sites)





























\hyperref[label_name]{''http://source.android.com/devices/tech/security/system-and-kernel-level-security"}



\hyperref[label_name2]{"http://link.springer.com/book/10.1007/978-1-4302-4063-1page-1"}

